First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-05-20 paper/paper.tex
Update paper todo
paper: Added a couple CCS tags and some description of motivation of the research

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2020}
\acmYear{2020}
\acmDOI{1}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Haskell '20]{Haskell '20: Proceedings of the 13th
  ACM SIGPLAN International Symposium on Haskell}{August 27 -- 28, 2020}{New Jersey, United States,}
\acmBooktitle{Haskell '20: ACM SIGPLAN International Symposium on Haskell,
  August 27 -- 28, 2020, New Jersey, United States}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10011007.10011006.10011050.10011017</concept_id>
       <concept_desc>Software and its engineering~Domain specific languages</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Domain specific languages}

@@

Readers who are primarily interested only in the encoding of pattern matching itself can direct
most of their attention to sections 2, 3 and 6.

@@

\begin{todo}
  Write
\end{todo}

@@

\clearpage
\section{Related Work}
\begin{todo}
  Cite and compare/contrast with pattern matching technique described in section
  3.3 of "Unembedding Domain-Specific Languages" (2009; Atkey, Lindley, Yallop)~\cite{Atkey:09:Unembedding}
\end{todo}

@@

\section{EDSL for C code generation}
\begin{lstlisting}
type CCode = String
type CName = String

>>>>

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.

\setcopyright{acmcopyright}
\copyrightyear{2020}
\acmYear{2020}
\acmDOI{1}

%% These commands are for a PROCEEDINGS abstract or paper.

\acmConference[Haskell '20]{Haskell '20: Proceedings of the 13th
  ACM SIGPLAN International Symposium on Haskell}{August 27 -- 28, 2020}{New Jersey, United States,}
\acmBooktitle{Haskell '20: ACM SIGPLAN International Symposium on Haskell,
  August 27 -- 28, 2020, New Jersey, United States}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10011007.10011006.10011041.10011046</concept_id>
       <concept_desc>Software and its engineering~Translator writing systems and compiler generators</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
   <concept>
       <concept_id>10011007.10011006.10011041.10011047</concept_id>
       <concept_desc>Software and its engineering~Source code generation</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
   <concept>
       <concept_id>10011007.10011006.10011050.10011017</concept_id>
       <concept_desc>Software and its engineering~Domain specific languages</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[300]{Software and its engineering~Translator writing systems and compiler generators}
\ccsdesc[300]{Software and its engineering~Source code generation}
\ccsdesc[500]{Software and its engineering~Domain specific languages}

% \begin{CCSXML}
% <ccs2012>
%    <concept>
%        <concept_id>10011007.10011006.10011050.10011017</concept_id>
%        <concept_desc>Software and its engineering~Domain specific languages</concept_desc>
%        <concept_significance>500</concept_significance>
%        </concept>
%  </ccs2012>
% \end{CCSXML}

% \ccsdesc[500]{Software and its engineering~Domain specific languages}

@@

Readers who are primarily interested only in the encoding of pattern matching itself can direct
most of their attention to Sections 2, 3 and 6. Most of the technical aspects of
the transformation performed by the Core plugin are described in Section 8.

@@

\begin{todo}
  Expand?
\end{todo}

A major benefit of the Haskell language is that you can often derive an
implementation from a specification, either partially or fully. When it is not
possible to fully derive an implementation from a specification, it is often
easier to check an implementation against a specification, due in part to the
management of side effects in Haskell. This is more difficult to do in
imperative languages like C or CUDA (as they provide no restrictions on where
side effects can occur).

Using Haskell EDSLs that allow the use of powerful language features like
pattern matching, these advantages can be brought to other domains where it is
currently either difficult or impossible to use Haskell.

\begin{todo}
  Cite examples. Conal Elliott's last two papers (the one about convolutions and
  the latest one about automatic differentiation), would probably be good
  examples of this in Haskell.

  A paper which describes a Haskell implementation of a specification given as
  an operational semantics would also be a good example.
\end{todo}

@@

\clearpage
\section{Related Work}
\begin{todo}
  Does this need more fleshing out?
\end{todo}

@@

\section{A small EDSL for C code generation used internally by the C backend}
\begin{lstlisting}
type CCode = String
type CName = String
